---
title: "Day 1 Interactive Session 2"
author: "Marie Rivers"
date: "8/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

### Logs and exponents in R

Some examples of using `log()` function and `exp()` function in R

*Note: use ' ' to get code style font (top left quote mark)

```{r}
# Examples of logarithms (used hashtag for comments)

log(4)

# Example of exponents

exp(5)

log(exp(1))
```
### Creating Sequences of Values

```{r}
# A sequence from 1 to 20, by increments of 1

ex_1 <- seq(from = 1, to = 20, by = 1)
# vector from 0 to 40 by increments of 0.2
ex_2 <- seq(from = 0, to = 40, by = 0.2)
#vector from 1 to 5000 by increments of 10
ex_3 <- seq(from = 1, to = 5000, by = 10)
```
### Create a function for logistic growth

Given the carrying capacity, initial population, the growth rate, and time, use the logistic growth model to estimate the population at that time.


```{r}
pop_logistic <- function(capacity, initial_pop, rate, time_yr) {
  
  capacity/(1 + ((capacity - initial_pop) / initial_pop) * exp(-rate * time_yr))
  
}
pop_logistic(capacity = 2580, initial_pop = 230, rate = 0.32, time_yr = 2.4)
  
# use squigle brackets { } when defining a function
```
### Try finding the population over a sequence of times

```{r}
time_vec <- seq(from = 0, to = 30, by = 0.5) 

```
Now let's estimate the population over that range of times, given capacity = 2580, initial population = 230, and rate = 0.31
```{r}
chipmunk_pop <- pop_logistic(capacity = 2580, initial_pop = 230, rate = 0.32, time_yr = time_vec)
```
### Create a data frame and plot chipmunk population over time

```{r}

chipmunk_df <- data.frame(time_vec, chipmunk_pop)

chipmunk_df  #call the data frame
```
### Create a bare minimum ggplot graph. 

First tell it you're using ggplot, then tell it what data you are using and what data you are plotting. Map a variable to an aesthetic. Tell the graph the type of geometry to create.
```{r}

ggplot(data = chipmunk_df, aes(x = time_vec, y = chipmunk_pop)) + 
  geom_point() +
  labs(x = "Time (years)",
      y = "Chipmunk population (individuals)",
      title = "Inyo National Forest Chipmunks",
      subtitle = "Yay chipmunks")
  #add axis labels and units with labs
```
```{r}
test = 5 + 7

```


